### 2021-03-01 newvariant.tex

Such inference also depends on assumptions about the underlying generation-interval distribution \citep{roberts2007model,svensson2007note,wallinga2007generation}.
Most studies have assumed that the generation-interval distributions do not differ between the existing strain and the variant, but recent evidence suggests that the new variant may have longer duration of infection: 13.3 days (90\% CI: 10.1--16.5) for the new variant and 8.2 days (90\% CI: 6.5--9.7) for the wild type \citep{kissler2021densely}.
Longer duration of infection is likely to provide opportunity to transmit for a longer period of time, meaning that the mean generation interval of the new variant is likely to be longer than that of the wild type.
More information is needed, however: generation intervals depend on many other biological and behavioral factors, including for example self-isolation after symptom onset leading .

>>>>

Such inference also depends on assumptions about the underlying generation-interval distribution \citep{roberts2007model,svensson2007note,wallinga2007generation}.
Most studies have assumed that the generation-interval distributions do not differ between the existing strain and the variant, but recent evidence suggests that the new variant may have longer duration of infection: 13.3 days (90\% CI: 10.1--16.5) for the new variant and 8.2 days (90\% CI: 6.5--9.7) for the wild type \citep{kissler2021densely}.
Longer duration of infection is likely to provide opportunity to transmit for a longer period of time, meaning that the mean generation interval of the new variant is likely to be longer than that of the wild type.
More information is needed, however: generation intervals depend on many other biological and behavioral factors, including for example self-isolation after symptom onset leading to shorter generation intervals.
